%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemSimple}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeMiniheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemSimple}[1]{\resumeItemSimple{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Arun Thiagarajan} & Email : \href{mailto:arunppsg@gmail.com}{arunppsg@gmail.com}\\
  \href{www.arunppsg.in}{www.arunppsg.in} & Github: \href{https://github.com/gusty1g}{gusty1g}\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PSG College of Technology}{Coimbatore, India}
      {Integrated Masters in Data Science;  GPA: 3.63 (9.08/10.0)}{July 2016 -- May 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://deepforestsci.com}{Deep Forest Sciences}}{Chennai, India}
      {Software Engineer}{Mar '22 - Present}
      \resumeItemListStart
        \item Worked on the design and development of Chiron - a compute platform for applying machine learning to drug discovery applications.
        \item Worked on product development, handling operations and deployments in AWS, testing via Github Actions and maintaining CI/CD pipelines.
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://github.com/deepchem/deepchem}{DeepChem}}{Chennai, India}
      {\href{https://github.com/deepchem/deepchem/pulls?q=is\%3Apr+author\%3Agusty1g+is\%3Aclosed}{Project Maintainer}}{June '21 - Present}
      \resumeItemListStart
        \item Implemented deep learning algorithms for use in drug discovery applications.
        \item Improved CI/CD pipelines, wrote unit tests and contributed to the project by improving code healthiness and documentation, performing code reviews and guiding new contributors.
      \resumeItemListEnd

    \resumeSubheading
      {Indian Institute of Technology, Madras}{Chennai, India}
      {Project Assistant}{Jan '21 - Feb '22}
      \resumeItemListStart
        \item Built a malware detection framework and implemented predictive modelling algorithms for detecting malware from network traffic data.
        \item Built packet logging tool which can capture and parse network packets at high speed (tested upto 50 MB/sec) and detect duplicate packets using a BloomFilter(\href{https://github.com/gusty1g/packet-sniffer}{code}).
      \resumeItemListEnd
     

    \resumeSubheading
      {Tata Consultancy Services}{Chennai, India}
      {Research and Development Intern}{May '19 - Nov '19}
      \resumeItemListStart
        \item Analyzed time series sales data and built time-series forecasting models for prediction future sales.
        \item Studied dynamic pricing algorithms based on reinforcement learning techniques for pricing perishable products.
      \resumeItemListEnd
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
    \resumeSubheading
      {in-d.ai}{Chennai, India}
      {Machine Learning Enginnering Intern}{June '20 - July '20}
      \resumeItemListStart
        \item Developed machine learning based solutions for classifying documents and extracting named entities. The solution was deployed using a Flask based web framework.
        \item Used IAM Handwriting dataset and augmented it to build a convolutional netural network for recognizing handwritten words to recognize handwritten characters.
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Others}
  \resumeSubHeadingListStart
    \resumeSubItemSimple {Awarded Achievement Award for outstanding curricular, co-curricular and extra-curricular achievements in MSc Data Science class of 2021.}
    \resumeSubItemSimple {Presented a \href{http://arunppsg.in/assets/files/healthcare_bias.pdf}{poster} on potential biases in using machine learning for healthcare applications.}
    \resumeSubItemSimple {Collected open data and performed a study on Food Corporation of India's operations highlighting challenges in providing food security(\href{http://arunppsg.in/assets/files/FCI.pdf}{analysis report}).}
    \resumeSubItemSimple {Taking Deep Generative Models course at the Center for Continuing Education, Indian Institute of Science, Bengaluru.}
    \resumeSubItemSimple {Given a talk about DeepChem at \href{https://www.youtube.com/watch?v=JEFrzjpf6d0}{Pycon India}, 2021 and \href{https://forum.fossunited.org/t/bangalore-foss-meetup-dec-2022/1397/6}{FOSS Meetup}.}
    \resumeSubItemSimple {Conducted \textit{Cricket and Statistics} program at Mango Education for kids aged between 11 - 15.}
  \resumeSubHeadingListEnd
%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Python, RStudio, C}
%      \hfill
%      \textbf{Technologies and Frameworks}{: MongoDb, MySQL, Pytorch, Scikit-Learn}
%    }
%  \resumeSubHeadingListEnd
%
%-------------------------------------------
\end{document}
